---
title: "HW1"
output: html_document
---

#Problem 1

Below is a dataframe containing four different vectors:

```{r prob1_df}

library(tidyverse)

prob1_df = tibble(
  rand_samp <- runif(10, min = 0, max = 5),
  log_vec <- c(rand_samp > 2),
  char_vec <- c(LETTERS[1:10]),
  fac_vec <- factor(c(LETTERS[1:10]))
)
```

Below is a random sample of size 10 from a uniform[0, 5] distribution.

```{r random_sample}

rand_samp <- runif(10, min = 0, max = 5)
```

Below is a logical vector indicating whether elements of the sample are greater than 2.

```{r logical_vec}

log_vec <- c(rand_samp > 2)
```

Below is a (length-10) character vector.
```{r char_vec}

char_vec <- c(LETTERS[1:10])
```

Below is a (length-10) factor vector.

```{r fac_vec}

fac_vec <- factor(c(LETTERS[1:10]))
```

Below is a dataframe containin all four vectors.

```{r dataframe}

df <- data.frame(rand_samp, log_vec, char_vec, fac_vec)
```

Below is the mean of each variable in the dataframe.

```{r means}

mean_rand_samp <- mean(rand_samp)
mean_log_vec <- mean(log_vec)
mean_char_vec <- mean(char_vec)
mean_fac_vec <- mean(fac_vec)
```

After taking the mean of each variable in my dataframe, it is evident that mean_rand_samp and mean_log_vec works because the arguments are numeric whereas mean_char_vec and mean_fac_vec are not.

Bellow is a code chunk that applies the as.numeric function to the logical, character, and factor variables.

```{r converting_to_num, eval = FALSE}

as.numeric(rand_samp)
as.numeric(new_log_vec)
as.numeric(char_vec)
as.numeric(fac_vec)
```

It is not possible to convert a character variable to a numeric vector which is why the output is NA for "as.numeric(char_vec)". It is possible to convert a factor vector to a numeric vector because the factor vector are categorical variables that assigns an integer to every unique level of a factor vector.

In this code chunk, the character variable (char_vec) is converted from character to factor to numeric; similarly, convert my factor variable (fac_vec) is converted from factor to character to numeric.

```{r converting_char_fac}

char_to_fac <- as.factor(char_vec)
as.numeric(char_to_fac)

fac_to_char <- as.character(fac_vec)
as.numeric(fac_to_char)
```

It is possible to convert a character vector to a factor vector to a numeric vector but it is not possible to convert a factor vector to a character vector to a numeric vector.

#Problem 2

Below is a dataframe for Problem 2:

```{r prob2_df}

library(tidyverse)

prob2_df = tibble(
  x <- rnorm(1000),
  y <- rnorm(1000),
  log_vec <- (x + y > 0),
  num_vec <- as.numeric(log_vec),
  fac_vec <- as.factor(num_vec)
)
```

Write a short description of your vector using inline R code, including: * the size of the dataset * the mean and median of x * the proportion of cases for which the logical vector is TRUE

Below is a scatterplot of y vs. x:

```{r scaterplot}

ggplot(prob2_df, aes(x = x, y = y)) +
  geom_point(aes(color = log_vec))
```

Make a scatterplot of y vs x; color points using the logical variable (adding color = ... inside of aes in your ggplot code should help). Make a second and third scatterplot that color points using the numeric and factor variables, respectively, and comment on the color scales.

Export your first scatterplot to your project directory using ggsave.
