---
title: "HW1"
output: html_document
---

#Problem 1

```{r vector_df}

library(tidyverse)

vector_df = tibble(
  rand_samp <- runif(10, min = 0, max = 5),
  log_vec <- c(rand_samp > 2),
  char_vec <- c(LETTERS[1:10]),
  fac_vec <- factor(c(LETTERS[1:10]))
)
```

Below is a random sample of size 10 from a uniform[0, 5] distribution.

```{r random_sample}

rand_samp <- runif(10, min = 0, max = 5)
```

Below is a logical vector indicating whether elements of the sample are greater than 2.

```{r logical_vec}

log_vec <- c(rand_samp > 2)
```

Below is a (length-10) character vector.
```{r char_vec}

char_vec <- c(LETTERS[1:10])
char_vec
```

Below is a (length-10) factor vector.

```{r fac_vec}

fac_vec <- factor(c(LETTERS[1:10]))
fac_vec
```

Below is a dataframe containin all four vectors.

```{r dataframe}

df <- data.frame(rand_samp,new_log_vec, char_vec, fac_vec)
df
```

Below is the mean of each variable in my dataframe.

```{r means, echo = FALSE, warning = FALSE}

mean_rand_samp <- mean(rand_samp)
mean_log_vec <- mean(log_vec)
mean_char_vec <- mean(char_vec)
mean_fac_vec <- mean(fac_vec)

mean_rand_samp
mean_log_vec
mean_char_vec
mean_fac_vec
```

After taking the mean of each variable in my dataframe, it is evident that mean_rand_samp and mean_log_vec works because the arguments are numeric whereas mean_char_vec and mean_fac_vec are not.

Bellow is a code chunk that applies the as.numeric function to the logical, character, and factor variables.

```{r converting_to_num, eval = FALSE}

as.numeric(rand_samp)
as.numeric(new_log_vec)
as.numeric(char_vec)
as.numeric(fac_vec)
```
It is not possible to convert a character variable to a numeric vector which is why the output is NA for "as.numeric(char_vec)". It is possible to convert a factor vector to a numeric vector because the factor vector are categorical variables that assigns an integer to every unique level of a factor vector.

In this code chunk, the character variable (char_vec) is converted from character to factor to numeric; similarly, convert my factor variable (fac_vec) is converted from factor to character to numeric.

```{r converting_other}

x <- as.factor(char_vec)
as.numeric(x)

y <- as.character(fac_vec)
as.numeric(y)
```

It is possible to convert a character vector to a factor vector to a numeric vector but it is not possible to convert a factor vector to a character vector to a numeric vector.

#Problem 2
